Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2021-12-03 analysis/paper_draft2.Rmd
edit paragraph describing coverage: change to "bias detection rate"

In turn, for three credible interval levels (80\%, 90\% and 95\%), we recorded the coverage rates, i.e., the proportion of times we can reach the correct conclusion about the bias parameter based on those credible intervals. That is, when the true value of $b_{curr}$ is greater than zero, the credible interval lies to the right of zero; when $b_{curr}$ equals to zero, the credible interval includes zero; and when $b_{curr}$ is less than zero, the credible interval lies to the left of zero. Since we use a weakly-informative prior that pulls the estimate of $b_{curr}$ towards zero, we focus not on how accurately the model can recover the true value of $b_{curr}$, but on how accurately our model can detect that bias. For instance, a 90\% coverage rate means that in 900 of 1000 model fits, a given credible interval contained what we fixed as the value of $b_{curr}$. Put another way, if we set $b_{curr}>0$, we calculate the proportion of the 90\% credible intervals that lie to the right of zero among the 1000 model fits.

>>>>

In turn, for three credible interval levels (80\%, 90\% and 95\%), we recorded the bias detection rates, i.e., the proportion of times we can reach the correct conclusion about the bias parameter based on those credible intervals. That is, when the true value of $b_{curr}$ is greater than zero, the credible interval lies to the right of zero; when $b_{curr}$ equals to zero, the credible interval includes zero; and when $b_{curr}$ is less than zero, the credible interval does not include zero. Since we use a weakly-informative prior that pulls the estimate of $b_{curr}$ towards zero, we focus _not_ on how accurately the model can recover the true value of $b_{curr}$ (i.e., a traditional coverage rate), but on how accurately our model can detect that bias. For instance, a 90\% bias detection rate means that in 900 of 1000 model fits, a given credible interval does not contain zero if the $b_{curr}$ is not zero. Put another way, if we set $b_{curr}>0$, we calculate the proportion of the 90\% credible intervals that lie to the right of zero (lower bound is positive) among the 1000 model fits.
